Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-20 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:20	22:20:19	(Thu20.Aug)

\begin{figure*}[tbhp!]\centering%
\includegraphics[width=\linewidth]{gfx/mvdr_selected_windows_holmengraa.pdf}%
\caption{Typical frequency responses for windows computed by a robust MVDR.\newline
Left:\hfill
\parbox[t]{.95\linewidth}{A sectorscan image of the oiltanker Holmengraa, using data collected from the 32 element HISAS1030 sonar attached to the HUGIN AUV. Image reconstructed with MVDR with $K=1$ temporal oversampling, $L=16$ subarray size and $d=1\%$ This is a sectorscan image with full opening angle 8 times lateral oversampling.}\newline
Right:\hfill
\parbox[t]{.95\linewidth}{The window responses was computed from 40x40 pixel groups in the shadow, highlight and speckle region. The dashed red lines at -13dB and -43dB marks the peak sidelobe level of a rectangular and Hamming window, respectively. Note how the responses are more or less symmetric, with very little steering in the shadow, moderate steering in speckle and steering within roughly 3dB in highlight. The phase varies mostly in highlight. Full opening angle. Parameters.} }\label{mvdr_selected_windows}
\end{figure*}

@@

To test the performance of the MVDR and LCA beamformers, we have processed data aquired by the Kongsberg Maritime HUGIN AUV carrying their 32 element HISAS1030 sonar~\cite{Hansen2009}. It is a high resolution synthetic aperture sonar with array length 1.2\;m, 100\;kHz operating frequency, a bandwidth of 40\;kHz and transmits at a 25$^\circ$ opening angle.

>>>>

\begin{figure*}[tbhp!]\centering%
\includegraphics[width=\linewidth]{gfx/mvdr_selected_windows_holmengraa.pdf}%
\caption{Typical frequency responses for windows computed by a robust MVDR.\newline
\emph{Left:}\hfill
\parbox[t]{.95\linewidth}{MVDR sectorscan image of the oiltanker Holmengraa, using data collected from the 32 element HISAS1030 sonar attached to the HUGIN AUV. MVDR was run with $K=1$ temporal oversampling, $L=16$ subarray size, $d=1\%$ diagonal loading and 8 times lateral oversampling.}\newline
\emph{Right:}\hfill
\parbox[t]{.95\linewidth}{Window responses computed from 40x40 pixel groups in the shadow, highlight and speckle region of the Holmengraa image. The dashed red lines at -13dB and -43dB marks the peak sidelobe levels of a rectangular and Hamming window, respectively. Note how the responses are more or less symmetric, with very little steering in the shadow, moderate steering in speckle and steering within roughly 3dB in highlight. The phase varies mostly in highlight.} }\label{mvdr_selected_windows}
\end{figure*}

@@

To test the performance of the MVDR and LCA beamformers, we have processed data aquired by the Kongsberg Maritime HUGIN AUV carrying their 32 element HISAS1030 sonar~\cite{Hansen2009}. It is a high resolution synthetic aperture sonar with array length 1.2\;m, 100\;kHz operating frequency, a bandwidth of 40\;kHz and 25$^\circ$ opening angle.
